Demographic Groups with Stronger Biden Support in the Election Races

### 2024-03-17 paper/paper.qmd
Final

ces2022_table <- ces2022 |>
  kable("html", booktabs = TRUE, caption = "Brief summary of variables types") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

print(ces2022_table)
```

@@

```
   After downloading `dataverse` [@dataverse], We using `get_dataframe_by_name` [@get_dataframe_by_name] to access the CES. We select and save the data that we are most care about, which are `votereg`, `presvote20post`, `race`, and `gender4`. `votereg` represent the voter registration status. To be more specific, whether they are registered to vote or not. `presvote20post` records the president that voter select in the election of 2020. “race" describe the voter's raical or ethnic group, and `gender4` refer to the gender of voters.
  However, when we access the raw data, there are some variables that we are not interested in. Therefore, we use the codebook to delve into the details. We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020. We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump. We use `tidyverse` [@tidyverse] to filter to the voters that we care about and label them with meaningful title. In addition，CES also provide the information for the gender of the voter. However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman. Therefore, we filter the gender by using `tidyverse` [@tidyverse]. When the variable `gender` is 1, this indicates "man", but we rename all "man" to "male". When the variable "gender" is 2, it refers to "woman". We also rename all "woman" to "female". Finally, the codebook also define different `race` from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other. We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
  To better understand the raw data, a summary table @fig-variables had been drawn in order to provide more details for each variables, explaining the variables we select. We select race and gender as the key variables that related to voter behavior. In @fig-vote, we can find the support data for both Biden and Trump based on the variables of gender and race.

>>>>

ces2022 |> slice_head(n = 10) |>
  kable(booktabs = TRUE, caption = "Brief summary of variables types") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

@@

```
   After downloading `dataverse` [@dataverse], We using `get_dataframe_by_name` to access the CES. We select and save the data that we are most care about, which are `votereg`, `presvote20post`, `race`, and `gender4`. `votereg` represent the voter registration status. To be more specific, whether they are registered to vote or not. `presvote20post` records the president that voter select in the election of 2020. “race" describe the voter's raical or ethnic group, and `gender4` refer to the gender of voters.
  However, when we access the raw data, there are some variables that we are not interested in. Therefore, we use the codebook to delve into the details. We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020. We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump. We use `tidyverse` [@tidyverse] to filter to the voters that we care about and label them with meaningful title. In addition，CES also provide the information for the gender of the voter. However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman. Therefore, we filter the gender by using `tidyverse` [@tidyverse]. When the variable `gender` is 1, this indicates "man", but we rename all "man" to "male". When the variable "gender" is 2, it refers to "woman". We also rename all "woman" to "female". Finally, the codebook also define different `race` from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other. We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
  To better understand the raw data, a summary table @fig-variables had been drawn in order to provide more details for each variables, explaining the variables we select. We select race and gender as the key variables that related to voter behavior. In @fig-vote, we can find the support data for both Biden and Trump based on the variables of gender and race.
